### 2019-09-01 paper/paper.tex
Edited down to results.

\subsection{Front Frame [H]}
%
The front frame is symmetric about the $XZ$ plane so $I_{Hxy}, I_{Hyz} = 0$. We
allow for any angular orientation of the $XZ$ principal directions but limit
the angle to $-\frac{\pi}{2} \leq \alpha_H \leq \frac{\pi}{2}$. We prevent the
rear frame from penetrating the ground by limiting the inertial spread with
respect to its mass center, $c_{13}$, but also set a minimum inertial spread to
ensure a frame can span from the rear wheel to the mass center of the rear
frame, $c_8$. The spread factor in $c_{13}$ of 1.4 is based on the ratio of
geometrical spread of a typical bicycle frame and its radius of gyration. The
front frame is not planar but is narrow with respect to the $XZ$ plane, which
is enforced by constraint $c_1$.

\subsection{Rear Frame [D]}
%
Several constraints are set for the rear frame. We constrain the rear frame to
be planar, $g_1$, and symmetric with respect to the $XZ$ plane. We prevent the
rear frame from penetrating the ground by limiting the inertial spread with
respect to its mass center, $c_{12}$, but also set a minimum inertial spread to
ensure a frame can span from the rear wheel to the mass center of the rear
frame, $c_9$. The spread factor in $c_{12}$ of 1.4 is based on the ratio of
geometrical spread of a typical bicycle frame and its radius of gyration.
Several parameters are bounded. We require the rear frame mass to be positive,
the center of mass not penetrate the ground, and we allow for any angular
orientation of the $XZ$ principal directions but limit the angle to
$-\frac{\pi}{2} \leq \alpha_D \leq \frac{\pi}{2}$ as angle beyond that are
redundant.

\subsection{Front [F] and Rear [R] Wheels}
%
We enforce the assumption that both wheels have moments of inertia of that of a
simple ring, $g_2 \ldots g_7$ and that mass and radius should be greater than a
minimal size based on small purchasable spoked wheel with tire.

@@

This translates to two constraints, $c_6,c_7$ that bound the total center of
mass $(x_T,z_T)$ in a triangle in the $XZ$ plane. Lastly, we constrain the
eight closed loop eigenvalues associated with the controller in~\cite{Hess2012}
to be stable, i.e. have negative real parts. These are expressed in
constraints $c_{14},\ldots,c_{21}$. Closed loop stability is required for the
HQM to provide a meaningful result.

@@

Our objective in the optimization is to minimize the peak HQM value subject to
the bounds, $\mathbf{p}^L,\mathbf{p}^U$, and the constraints
$\mathbf{g}(\mathbf{p}),\mathbf{c}(\mathbf{p})$ . Given a set of bicycle model
parameter values we generate a bandwidth limited human-like controller using
the methods in ~\cite{Moore2012}. Once the closed loop stable controller is
constructed, the HQM can be computed as per the definition in \cite{Hess2012}
and the scaler peak value returned as the objective $J$. This problem is
presented as a non-linear programming problem in the following equation.
%
\begin{equation}
  \begin{aligned}
    & \underset{\mathbf{p}}{\text{minimize}} & & J(\mathbf{p})=max(\textrm{HQM}(\mathbf{p})) \\
    & \text{subject to} & & \\
    & & & \mathbf{g}(\mathbf{p}) \leq \mathbf{0} \\
    & & & \mathbf{c}(\mathbf{p}) = \mathbf{0} \\
    & & & \mathbf{p}^L \leq \mathbf{p} \leq \mathbf{p}^U
  \end{aligned}
\end{equation}

>>>>

\subsection{Front Frame [H]}
%
The front frame is symmetric about the $XZ$ plane so $I_{Hxy}, I_{Hyz} = 0$. We
allow for any angular orientation of the principal directions in the $XZ$ plane
but limit the angle to $-\frac{\pi}{2} \leq \alpha_H \leq \frac{\pi}{2}$. We
prevent the rear frame from penetrating the ground by limiting the inertial
spread with respect to its mass center, $c_{13}$, but also set a minimum
inertial spread to ensure a frame can span from the rear wheel to the mass
center of the rear frame, $c_8$. The spread factor in $c_{13}$ of 1.4 is based
on the ratio of geometrical spread of a typical bicycle frame and its radius of
gyration. The front frame is not planar due to the need for handlebars
protruding in the $Y$ direction so we only ensure consistent moments of inertia
with $c_1$.

\subsection{Rear Frame [D]}
%
Several constraints are set for the rear frame. We constrain the rear frame to
be planar, $g_1$, and symmetric with respect to the $XZ$ plane. We prevent the
rear frame from penetrating the ground by limiting the inertial spread with
respect to its mass center, $c_{12}$, but also set a minimum inertial spread to
ensure a frame can span from the rear wheel to the mass center of the rear
frame, $c_9$. The spread factor in $c_{12}$ of 1.4 is based on the ratio of
geometrical spread of a typical bicycle frame and its radius of gyration.
Several rear frame parameters are bounded. We require the rear frame mass to be
positive, the center of mass not penetrate the ground, and we allow for any
angular orientation of the principal directions in the $XZ$ plane but limit the
angle to $-\frac{\pi}{2} \leq \alpha_D \leq \frac{\pi}{2}$ as angle beyond that
are redundant.

\subsection{Front [F] and Rear [R] Wheels}
%
We enforce the assumption that both wheels have moments of inertia of that of a
simple ring, $g_2 \ldots g_7$ and that the mass and radius should be greater
than a minimal size based on small purchasable spoked wheel with tire.

@@

This translates to two constraints, $c_6,c_7$ that bound the total center of
mass $(x_T,z_T)$ in a triangle in the $XZ$ plane. Lastly, we constrain the
eight closed loop eigenvalues associated with the controller in~\cite{Hess2012}
to be stable, i.e. have negative real parts. These are expressed in constraints
$c_{14},\ldots,c_{21}$. Closed-loop stability is required for the HQM to
provide a meaningful result, see~\cite{Hess2012} for an explanation.

@@

Our objective in the optimization is to minimize the peak HQM value subject to
the bounds, $\mathbf{p}^L,\mathbf{p}^U$, and the constraints
$\mathbf{g}(\mathbf{p}),\mathbf{c}(\mathbf{p})$ . Given a set of bicycle model
parameter values we generate a bandwidth limited human-like controller using
the methods in~\cite{Moore2012}. Once the closed-loop stable controller is
constructed, the HQM can be computed as per the definition in~\cite{Hess2012}
and the scaler peak value returned as the objective $J$. This problem is
presented as a non-linear programming problem in the following equation.
%
\begin{equation}
  \begin{aligned}
    & \underset{\mathbf{p}}{\text{minimize}} & & J(\mathbf{p})=max(\textrm{HQM}(\mathbf{p})) \\
    & \text{subject to} & & \\
    & & & \mathbf{g}(\mathbf{p}) \leq \mathbf{0} \\
    & & & \mathbf{c}(\mathbf{p}) = \mathbf{0} \\
    & & & \mathbf{p}^L \leq \mathbf{p} \leq \mathbf{p}^U
  \end{aligned}
\end{equation}
